Improving the Replicability of Psychological Science Through Pedagogy

### 2017-06-27 paper/paper.Rmd
mcf pass

Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012]. Yet under the current incentive structure for science, replication is not typically valued valued for publication [@makel2012], or in metrics of research productivity [@koole2012]. One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012]. Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy in producing wide-scale pedagogical adoption.

@@

We also describe our process for conducting replications as part of classroom pedagogy. Although mentorship in experimental methods is an important part of the standard advising relationship, the classroom context allows for elucidation of general principles of good research and discussion of how they can be modified to fit specific instances. And replication research in particular illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- more directly than open-ended projects, which require new conceptual development [see @frank2012 for extended argument]. There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise. Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole---both scientific and educational---would be considerable.

@@

To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4/files/](https://osf.io/98ta4/files/). In addition, all of the most recent lecture slides and materials are avaialable on our course website at [http://psych254.stanford.edu](). We hope that others will share and reuse our materials as they consider how best to design a course customized to their context.

@@

As described below, our procedure for individual project preregistrations was to register the analytic script with specific key hypothesis tests clearly marked. Individual project preregistration links are given in Table 1. Prior to data collection for all projects, we also pre-registered the confirmatory analyses reported in the current paper ([https://osf.io/rxz8m/](https://osf.io/rxz8m/)).

@@

All code and data necessary to reproduce the analyses reported here are available at: [https://osf.io/98ta4](https://osf.io/98ta4).

@@

Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class. We are grateful to the authors of the original studies who provided materials and gave comments on a draft of this manuscript.

@@

Students used JavaScript and HTML/CSS to reimplement their respective target studies in the web browser, following the materials and methods specified by the original authors as closely as possible.
Of the `r nrow(d)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available. 
For `r sum(project_plan$author_contact != "")` studies, however, students contacted the authors to request either materials or clarification of methods using a template email that was customized by the students and reviewed by the instructors (this template is included in our course materials). 
Responses were received in all but one case, all within a matter of days.

## Preregistration and Review

In addition to as-needed guidance on projects, students advanced through a formal review process in which each student's work was inspected and critiqued several times by both the instructor (MCF) and the teaching assistants (ENS and RXDH). 
After selecting their replication targets, students' first milestone was to fill in the methods section of the @osc2015 replication report template, which was reviewed for feasability and concreteness. 
This section included a power analysis, proposed sample size, and explicit description of differences from the original study (see course materials for complete template).

@@

Despite the general emphasis in meta-analytic and reproducibility efforts on aggregating a single effect size of interest [@osc2015;@lipsey2001], it was often challenging for us to identify a single key statistical test for each study. Usually a substantial number of statistical tests were conducted, often within one or several regression models with multiple specifications. Thus, we interpret "key statistical test" results with caution (see Empirical Results and Discussion below). Despite this interpretive difficulty, following previous work, we attempted to use a single statistical test as our target for replication planning and analysis.

@@

Above we have shown that classroom replication projects are possible. We now present information that we hope will reduce barriers to entry and encourage more researchers and instructor to include replications as part of coursework.  This includes practical recommendations for implementation in a variety of classroom, key decision that instructors must make, and common issues that may arise throughout the projects and ways to mitigate or prevent these issues.

@@

That said, we beleive there are many ways to adapt the project format based on the students and constraints of the class.  In Table \ref{tab:classmodels} below, we present mulitple ways in which replication projects may be included in classrooms.  Though we do not go into detail on all of the specifics of what each of these courses might entail, we hope this provides an overview of the possibilities inherent in including replication work as part of student learning.  We next turn to detailed discussion on a subset of aspects we believe most pertinent to instructors.

@@

\begin{tabular}{l|lll}

@@

\multicolumn{1}{p{1.5in}|}{\raggedright \underline{Course Attributes}} & \underline{Model 1} & \underline{Model 2} & \underline{Model 3} \\

Students & \multicolumn{1}{p{2in}}{\raggedright Undergraduate} & \multicolumn{1}{p{2in}}{\raggedright Advanced Undergraduate or Early Graduate} & \multicolumn{1}{p{2in}}{\raggedright Motivated Graduate} \\

Learning Goal & \multicolumn{1}{p{2in}}{\raggedright Gain experience with research process} & \multicolumn{1}{p{2in}}{\raggedright Conduct collaborative research} & \multicolumn{1}{p{2in}}{\raggedright Learn best practices and tools} \\

Project Grouping & \multicolumn{1}{p{2in}}{\raggedright Full Class or Medium-sized groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individual} & \multicolumn{1}{p{2in}}{\raggedright Individual} \\

Project Selection & \multicolumn{1}{p{2in}}{\raggedright One class replication or pre-specified list} & \multicolumn{1}{p{2in}}{\raggedright Curated list to choose from} & \multicolumn{1}{p{2in}}{\raggedright Open to student choice*} \\

@@

Workflow tools & \multicolumn{1}{p{2in}}{\raggedright Use familiar or GUI tools or instructors implement studies} & \multicolumn{1}{p{2in}}{\raggedright Teach key open-source tool plus introduce others} & \multicolumn{1}{p{2in}}{\raggedright Teach full set of free open-source software} \\

Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\

@@

Dissemination & \multicolumn{1}{p{2in}}{\raggedright If up to quality standard} & \multicolumn{1}{p{2in}}{\raggedright Upon review of instructors} & \multicolumn{1}{p{2in}}{\raggedright Discuss dissemination as a class} \\

\end{tabular}
\caption{\label{tab:classmodels} The potential models for incorporating replication studies in required coursework. *This can also be done with a systematic sampling strategy} 
\label{tab:classmodels}
\end{table}

@@

In our class, students selected projects based on interest, rather than via a systematic sampling strategy. After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility. We encouraged students with little programming background to opt for methodologically simple studies, and more advanced students to take on a challenging design. However, this sample also reflects what is of most interest to beginning researchers, and we suspect may be a better sampling frame to better understand particularly impactful effects to be built upon in future research. The modal study chosen was the first, but several students chose later studies in a set as well.  Thus, all interpretation of our findings should be with respect to this non-probability sample.  This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.

The set of studies could be curated more or less for students based on expertise and constraints.  For example, in a large undergraduate class it may be logistical simpler for the instructors to choose 1-3 replication projects that students can select from. This would allow the instructor to be familiar with all replication projects taking place, and provide more structured discussion and problem-solving based on the challenges groups may run into.

@@

Over half of our students reached out to original authors to request study materials or clafication on methods and/or analysis.  For the purposes of this class, we chose not to require contact with all original authors. We strongly believe methods and materials should be open to allow for replication and productive science [@nosek2015], and hoped to make students feel empowered that they can engage with and build on the published literature directly.  That is, we chose to do good-faith replications given all information in the original articles and supplemental online materials.  Only in cases where there were issues about access to materials or ambiguities in design or analysis were authors contacted.

However, we acknowledge there are benefits of contacting all original authors.  There are two main methods of doing so. First is as a professional courtesy by letting the authors know that their study is being replicated.  This not only provides goodwill (as replication are perceived by some to be adversarial; see Kahneman commentary?), it would also allow the original authors to pre-register their hypotheses or concerns with the replication study as experts in the underlying theory. Second is as a request for methodological feedback prior to replication. This is a trickier issue on many fronts.  By requesting feedback, this perpetuates insider information or lab-specific folklore on methodology that produces the greatest effects. When these assumptions or limitations of a theory or paradigm are not made explicit in publically-available format, this does not count as a record of science. In fact, some replications have prompted these assumptions to be made explicit by the original authors (CITE?).  In addition, when original materials of a study are not provided, it is on the reader to assume all neccessary information is provided to replicate, and is not due to idiosyncracies. Thus, we would generally advice against contacting authors for feedback or materials expect when replication is not viable without them.

@@

We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies. This choice was made to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge. Our general class structure does not depend on the use of AMT, however, and the use of this particular online sample should be viewed as limiting the interpretation of some results. Other classes many find participant pools or recruitment of community samples more feasible and appropriate.

Repeat administration of empirical work on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge. We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses. In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).

As much of psychological research is now conducted online and we know of few graduate programs that require explicit training in online programming and methods, an additional pedagogical benefit of conducting online replications is to build competence in these skills.  Even if students’ research does not generally consist of online studies, these replications allow students to build a skillset that can be utilized throughout their academic careers.

@@

Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015]. Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for studies that were initially large and/or adequately powered.

In this set of replications, we opted for a case-by-case weighing of the costs and benefits of increasing power across all studies. Though we discussed these allocations and bartered allocations as a class, we had a few guiding principles. We first prioritized achieving the participants required for either 80% or original N (whichever was greater) for the maximum number of studies. This benefitted studies which were under the budget allocated for each individual project (i.e. studies that had large effect sizes and short participation times.)  Of those that achieved 80% power with sample sizes that were smaller than the original sample, we reduced the most expensive studies down to N required for 80% power. This allowed us to reach our budget goals with the exception of one particularly expensive study.  Fortunately, this student found external funding to reach 80% power. If this were not possible, we would have likely excluded this study from the pre-registration.

@@

Finally, one of the barriers to more reproducible work in psychology is technical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners. Indeed, our students, who came from a variety of disciplinary backgrounds, had relatively little experience with web-based empirical studies or literate, reproducible data analysis. Yet by the end of the course, all had gained sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently. This experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environment -- students can quickly learn to use a reproducible toolset.

All replication studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser. All analyses were written using R, a free and open-source platform for statistical analysis.  Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document.

Using the template developed by @osc2015 for replication reports (included in our course materials), students first specified the scope and methods of their proposed replication study, including any differences from the original methods. Later, they added the code necessary to analyze their data, and after collecting their full sample, the results of their data analysis (e.g., statistical tests and figures). This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.

@@

Institutional Review Boards are idiosyncratic across institutions, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.  We address just two, with potential resolutions and comments.

Instructors may first be concerned that IRB approval is not possible within the time constraints of the class.  To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine how to either 1) create a standard protocol that encompassses all replications that will be conducted (in which details can be later added and quickly approved), or 2) plan to submit the protocol early in the course, in line with IRB meeting schedules for quick turnarounds. Both issues may be simplified if the study or pool of studies to be replicated is pre-determined and if these studies provide full open-source materials that can be used in the IRB protocol submitted.

In addition, instructors and review boards may believe there is a greater potential for harm given constraints of class. That is, there may be less oversight to each individual project.  However, we note that especially if the original studies have been previously approved by their respective institutional review board, the review process is similar to one might expect out of an advisee/advisor relationship. Particular consideration should be given to concerns of confidentiality of collected data, and we may suggest that for less experienced students, identifiable participant data should only be accessed by the instructor team.  Lastly, this project can also be a useful tool to have class discussions around coersion, harm vs. benefit, and other ethical issues that may arise during reserach.

@@

All reported results are from pre-registered, confirmatory analyses.

**rxdh: re: Dan Simons' comment about the results being cumbersome w/o Table 1 showing individual replication outcomes, maybe we should explicitly state our motivation behind presenting these results and say something along the lines of "to avoid targeting particular authors for potential criticism on the basis of a single replication, we only present summary evaluations aggregated across our replications"**

**rxdh: this next paragraph seems a bit minor and might be better in a footnote?**

In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim. In both of these cases, the original authors had fit regression models to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis. After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest. We report results from these corrected tests here. We return to this issue in the Discussion, as we believe that test selection is a critical theoretical issue in replication research [see e.g., @monin2016 for discussion].

@@

In addition, our statistical findings mask a more optimistic message: In most of our projects, the next step for a motivated experimenter is clear. For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials. In others, the difficulty appeared to be statistical power, since differences were in the predicted direction and sometimes reached significance in subsidiary analyses, so a followup would likely require a larger sample. And in some, differences of population would mean that followups would require further stimulus or task adaptation. More generally, we believe that our work here underscores the importance of iterated replication for pinpointing empirical effects and refining theories [see e.g., @lewis2016 for an example of this strategy and some discussion].

Many statistical factors leading to lowered replicability have been discussed in past work, including analytic flexibility, context dependency, publication bias, and low statistical power among others [e.g., @button2013; @vanbavel2016; @ioannidis2005]. For both reasons of design and scale, our study here cannot disentangle these factors empirically. Nevertheless, the decreases in effect size and evidential value we report seem consistent with two explanations. First, we likely saw a "winner's curse," with initial publications tending to over-estimate effects. Second, we also might have seen a reduction in effect size because the original studies were tailored to their specific context and population, whereas our replications may not have been [@vanbavel2016, but cf. @inbar2016]. Future work would benefit from a statement of constraints on generality so as to provide a guide to the conditions under which an effect is likely to be present [@simons2016]. Both of these explanations are consistent with our observations, and, based on the previous literature [@osf2015,@vanbavel2016], we speculate that both winner's curse and context effects were present to some degree.

@@

In our view, two recommendations will improve this situation. First, authors should specify their "key test" more clearly. Pre-registration might facilitate this step, as regstration typically requires the selection of particular statistical analyses to be designated as critical for interpretation, but we believe this designation is critical even in un-registered experiments. Had "key test" information been available, it would have dramatically simplified the problem of selecting the effect to replicate in several cases. Second, the widespread adoption of open data and open analytic code practices would facilitate replication research. In addition to clarifying the summary report of results in a paper, the availability of data dramatically facilitates the computation of the relevant meta-analytic effect size for power analysis and statistical comparison.^[We note that, although we were grateful that several authors of the papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.]

>>>>

Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012]. Yet under the current incentive structure for science, replication is not typically valued for publication [@makel2012] or in metrics of research productivity [@koole2012]. One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012]. Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy in producing wide-scale pedagogical adoption.

@@

We also describe our process for conducting replications as part of classroom pedagogy. Although mentorship in experimental methods is an important part of the standard advising relationship, the classroom context allows for elucidation of general principles of good research and discussion of how they can be modified to fit specific instances. And replication research in particular illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- more directly than open-ended projects, which require new conceptual development [see @frank2012 for extended argument]. There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise. Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole -- both scientific and educational -- would be considerable.

@@

To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4/files/](https://osf.io/98ta4/files/). In addition, all of our most recent lecture slides and materials are avaialable on our course website at [http://psych254.stanford.edu](). We hope that others will share and reuse our materials as they consider how best to design a course customized to their context.

@@

As described below, our procedure for individual project preregistrations was to register the analytic script with specific key hypothesis tests clearly marked. Individual project preregistration links are given in Table 1. Prior to data collection for all projects, we also pre-registered the confirmatory analyses reported in the current paper at [https://osf.io/rxz8m/](https://osf.io/rxz8m/).

@@

All code and data necessary to reproduce the analyses reported here are available at [https://osf.io/98ta4](https://osf.io/98ta4).

@@

Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class. We are grateful to the authors of the original studies who provided materials and gave extensive comments on an earlier draft of this manuscript.

@@

Students used JavaScript and HTML/CSS to reimplement their respective target studies in the web browser, following the methods specified by the original authors as closely as possible.
Of the `r nrow(d)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available. 
For `r sum(project_plan$author_contact != "")` studies, students contacted the authors to request either materials or clarification of methods using a template email that was customized by the students and reviewed by the instructors (this template is included in our course materials). 
Responses were received in all but one case, all within a matter of days.

## Writing, Preregistration, and Review

Using the template developed by @osc2015 for replication reports (included in our course materials), students first specified the scope and methods of their proposed replication study, including any differences from the original methods. Later, they added the code necessary to analyze their data, and after collecting their full sample, the results of their data analysis (e.g., statistical tests and figures). This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors (@nuijten2015), given that errors are often introduced by transferring results between statistics and word-processing software packages.]

In addition to as-needed guidance on projects, students advanced through a formal review process in which each student's work was inspected and critiqued several times by both the instructor and the teaching assistants. After selecting their replication targets, students' first milestone was to fill in the methods section of the @osc2015 replication report template, which was reviewed for feasability and concreteness. This section included a power analysis, proposed sample size, and explicit description of differences from the original study (see course materials for complete template).

@@

Despite the general emphasis in meta-analytic and reproducibility efforts on aggregating a single effect size of interest [@osc2015;@lipsey2001], it was often challenging for us to identify a single key statistical test for each study. Usually a substantial number of statistical tests were conducted, often within one or several regression models with multiple specifications. Thus, we interpret "key statistical test" results with caution (see Empirical Results and Discussion below). Despite this interpretive difficulty, we followed previous work and attempted to use a single statistical test as our target for replication planning and analysis.

@@

Our findings demonstrate that classroom replication projects are possible in one particular context. In the following subsections, we provide information that we hope will reduce barriers to entry and encourage more researchers and instructor to include replications as part of coursework in their courses. We discuss practical recommendations for implementation in a variety of classroom settings, key decisions that instructors must make, and common issues that arise during replication projects.

@@

That said, depending on the student population and class constraints, there are many ways to include a replication project in a course. Table \ref{tab:classmodels} presents three different possible models of replication projects, for general undergraduate classes, advanced undergraduate/early graduate classes, and more advanced graduate classes. These models are not meant to be binding suggestions, but we hope that they inspire instructors to consider how replication research could be included in their own teaching practice. The sections below provide some discussion of individual choice-points.

@@

\begin{tabular}{lccc}

\multicolumn{1}{p{1.5in}}{\raggedright \underline{Course Attributes}} & \underline{Model 1} & \underline{Model 2} & \underline{Model 3} \\

Student group & \multicolumn{1}{p{2in}}{\raggedright General Undergraduate} & \multicolumn{1}{p{2in}}{\raggedright Advanced Undergraduate or Graduate} & \multicolumn{1}{p{2in}}{\raggedright Sophisticated Graduate} \\

@@

Learning goal & \multicolumn{1}{p{2in}}{\raggedright Gain experience with research process} & \multicolumn{1}{p{2in}}{\raggedright Gain research independence} & \multicolumn{1}{p{2in}}{\raggedright Master best practices and tools} \\

Group size & \multicolumn{1}{p{2in}}{\raggedright Full class / medium-size groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individuals} & \multicolumn{1}{p{2in}}{\raggedright Individual} \\

Project selection & \multicolumn{1}{p{2in}}{\raggedright Single class replication or small curated list} & \multicolumn{1}{p{2in}}{\raggedright Curated list} & \multicolumn{1}{p{2in}}{\raggedright Open project selection*} \\

@@

Workflow tools & \multicolumn{1}{p{2in}}{\raggedright Use GUI tools / instructors implement studies} & \multicolumn{1}{p{2in}}{\raggedright Teach one key open-source tool (e.g., R)} & \multicolumn{1}{p{2in}}{\raggedright Teach full ecosystem of key open-source tools} \\

<!-- Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\ -->

@@

Dissemination & \multicolumn{1}{p{2in}}{\raggedright If meeting pre-specified quality standard} & \multicolumn{1}{p{2in}}{\raggedright With instructor approval} & \multicolumn{1}{p{2in}}{\raggedright As class default (subject to disucssion)} \\

\end{tabular}
\caption{\label{tab:classmodels} Three potential models for incorporating replication projects into classes of different levels.} 
\label{tab:classmodels}
\end{table}

@@

In our class, students selected projects based on interest, rather than via a systematic sampling strategy. After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility. We encouraged students with little programming background to opt for methodologically simple studies, and more advanced students to take on a challenging design. This level of freedom is not ideal for less advanced courses, and the set of available replication studies should likely be curated for students at other levels.  For example, in a large undergraduate class it may be logistically simpler for the instructors to choose 1 -- 3 replication projects that students can select from. This step would both give instructors a greater degree of familiarity with the literature and allow for the development of more scaffolding with respect to the development of experimental materials. A mid-level course might split the difference between these two models, providing students with a broader -- but still curated -- list of potential projects.

<!-- However, this sample also reflects what is of most interest to beginning researchers, and we suspect may be a better sampling frame to better understand particularly impactful effects to be built upon in future research. The modal study chosen was the first, but several students chose later studies in a set as well.  Thus, all interpretation of our findings should be with respect to this non-probability sample.  This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students. -->

@@

Over half of our students contacted original authors to request study materials or clafication on methods and/or analysis, but for the purposes of our class, we chose not to require contact with all original authors. We strongly believe methods and materials should be open to allow for replication and productive science [@nosek2015], and hoped to empower students to engage with and build on the published literature directly -- without personal relationships or even personal contact. That is, we chose to do good-faith replications given all information in the original articles and supplemental online materials. Authors were contacted only in cases where there were issues about access to materials or ambiguities in design or analysis. There are benefits of contacting original authors, however. In addition to professional courtesy, authors can provide valuable feedback or guidance (albeit at the cost of some imposition). In the end, it is up to individual instructors to decide what they believe is best for their students.

<!-- First, contact is a professional courtesy that lets the authors know that their study is being replicated and in some cases allows the original authors to pre-register their hypotheses or concerns with the replication study. Second, original authors can provide methodological feedback prior to replication. This second is a trickier issue on many fronts.  By requesting feedback, discussion with authors perpetuates the dissemination of insider information or lab-specific folklore on methodology that produces the greatest effects. When these assumptions or limitations of a theory or paradigm are not made explicit in publically-available format, this does not count as a record of science. In fact, some replications have prompted these assumptions to be made explicit by the original authors (CITE?).  In addition, when original materials of a study are not provided, it is on the reader to assume all neccessary information is provided to replicate, and is not due to idiosyncracies. Thus, we would generally advice against contacting authors for feedback or materials expect when replication is not viable without them. -->

@@

We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies.^[Repeat administration of empirical work on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge. We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses due to failures to distinguish between related experimental paradigms. In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).] This choice was made to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge. As much of psychological research is now conducted online, an additional pedagogical benefit of conducting online replications is to build competence in these skills. Even if students’ current research does not use AMT, these replications allow students to build a skillset that can be used throughout their academic careers. Our general class structure does not depend on the use of AMT, however, and the use of this particular online sample should be viewed as limiting the interpretation of some of our results. Other classes many find participant pools or recruitment of community samples more feasible and appropriate.

@@

Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015]. Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013]. But -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases. For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for studies that were initially large and/or adequately powered. In general, samples for course projects will be limited by the available resources. But for all replication research of the type advocated here, achieving high power for a smaller number of studies, perhaps conducted by groups, is preferable to conducting more lower-power studies, because results are much more likely to make a contribution to the replication literature (as well as to be interpretable by students). Regardless of the eventual sample collected, we find that the discussion of sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in the planning process.

<!-- In our replications, we opted for a case-by-case weighing of the costs and benefits of increasing power across all studies. We first prioritized achieving the participants required for either 80% or original N (whichever was greater) for the maximum number of studies. This rule benefitted studies which were under the budget allocated for each individual project (i.e., studies that had large effect sizes and short participation times.)  Of those that achieved 80% power with sample sizes that were smaller than the original sample, we reduced the most expensive studies down to N required for 80% power. This allowed us to reach our budget goals with the exception of one particularly expensive study.  Fortunately, this student found external funding to reach 80% power. If this were not possible, we would have likely excluded this study from the pre-registration. -->

@@

All our studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser. All analyses were written using R, a free and open-source platform for statistical analysis.  Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document.

Some of these tools can feel inaccessible or intimidating to beginners. Indeed, our students, who came from a variety of disciplinary backgrounds, typically have relatively little experience with web-based empirical studies or literate, reproducible data analysis. Yet by the end of the course, all gain sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently. Our experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environment -- students can quickly learn to use a reproducible toolset.

Our explicit class goal was to provide students with experiences navigating the full ecosystem of open-source scientific tools. For classes at different levels, however, instructors will likely have different goals. It may be preferrable for an intermediate course to focus on a single programming tool (e.g., R) and to use other GUI-based software for creating experiments, so as to minimize the learning burden for students. And for more introductory research methods course, instructors must gauge whether the added difficulty of a programming compoent is appropriate for the skills and backgrounds of their students.

@@

Institutional Review Boards (IRBs) are idiosyncratic across institutions, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects. First, instructors may first be concerned that IRB approval is not possible within the time constraints of the class.  To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine whether to create a standard protocol that encompassses all replications that will be conducted, or to determine a timeline for submitting individual protocols very early in the course. Both issues may be simplified if the study or pool of studies to be replicated is pre-selected by instructors. Second, review boards may be concerned about risks particular to the collection of data by students, e.g., lack of debriefing or greater risk of breach of confidentiality due to novice experimenters. We recommend building training around ethical issues into the syllabus of replication-based classes. This practice is both positive for studetns and mitigates potential IRB concerns via explicit training.

@@

All reported results are from pre-registered, confirmatory analyses.^[In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim. In both of these cases, the original authors had fit regression models to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis. After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest. We report results from these corrected tests here. We return to this issue below, as we believe that test selection is a critical theoretical issue in replication research (see e.g., @monin2016 for discussion).]

<!-- **rxdh: re: Dan Simons' comment about the results being cumbersome w/o Table 1 showing individual replication outcomes, maybe we should explicitly state our motivation behind presenting these results and say something along the lines of "to avoid targeting particular authors for potential criticism on the basis of a single replication, we only present summary evaluations aggregated across our replications"** MCF: let's say this in the coverletter? -->

<!-- **rxdh: this next paragraph seems a bit minor and might be better in a footnote?** -->

@@

Our statistical findings mask a more optimistic message: In most of our projects, the next step for a motivated experimenter is clear. For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials. In others, the difficulty appeared to be statistical power, since differences were in the predicted direction and sometimes reached significance in subsidiary analyses, so a followup would likely require a larger sample. And in some, differences of population would mean that followups would require further stimulus or task adaptation. More generally, we believe that our work here underscores the importance of iterated replication for pinpointing empirical effects and refining theories [see e.g., @lewis2016 for an example of this strategy and some discussion].

Many statistical factors leading to lowered replicability have been discussed in past work, including analytic flexibility, context dependency, publication bias, and low statistical power among others [e.g., @button2013; @vanbavel2016; @ioannidis2005]. For both reasons of design and scale, our study here cannot disentangle these factors empirically. Nevertheless, the decreases in effect size and evidential value we report seem consistent with two explanations. First, we likely saw a "winner's curse," with initial publications tending to over-estimate effects. Second, we also might have seen a reduction in effect size because the original studies were tailored to their specific context and population, whereas our replications may not have been [@vanbavel2016, but cf. @inbar2016]. Future work would benefit from a statement of constraints on generality so as to provide a guide to the conditions under which an effect is likely to be present [@simons2016]. 
<!-- Both of these explanations are consistent with our observations, and, based on the previous literature [@osf2015,@vanbavel2016], we speculate that both winner's curse and context effects were present to some degree. -->

@@

<!-- In our view, two recommendations will improve this situation. First, authors should specify their "key test" more clearly. Pre-registration might facilitate this step, as regstration typically requires the selection of particular statistical analyses to be designated as critical for interpretation, but we believe this designation is critical even in un-registered experiments. Had "key test" information been available, it would have dramatically simplified the problem of selecting the effect to replicate in several cases. Second, the widespread adoption of open data and open analytic code practices would facilitate replication research. In addition to clarifying the summary report of results in a paper, the availability of data dramatically facilitates the computation of the relevant meta-analytic effect size for power analysis and statistical comparison.^[We note that, although we were grateful that several authors of the papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.]  -->
